A self-consistency check for unitary propagation of Hawking quanta

### 2016-08-13 Draft_BH_shells.tex
updated appendix with new results

Classically, soft hairs manifest as memory effects that alters the distances between geodesics, which is very similar to the effect of geometric uncertainty as we showed in this paper.
Based on this picture, one may try to quantize the soft hairs and build a toy model that invovles quantum interaction, therefore entanglement, between the soft hairs and the usual QFT modes.
That would provide a complete picture that the loss of subsystem unitarity is really just entanglement with another subsystem which was originally (and illegitimately, as we argued) assumed as the classical background.

@@

where the superscript represents particle $1$ so $\bar{t_e}^{(1)}$ represents the time at which particle $1$ is emitted, $\bar{t_0}^{(1)}$ is when particle 1 is observed. Analogously for a particle $2$ that is emitted at $\bar{t_e}^{(2)}$ we have

@@

We can convert $\delta\bar{t_0}$ to proper time

\begin{equation}
	\delta \bar{\tau_0} = \left( 1 -\frac{2M}{r_0} \right)^\frac{1}{2} \delta \bar{t_0}
\end{equation}

and in the limit that the observer is very far away $\delta \bar{\tau_0} \approx \delta \bar{t_0}$.

@@

Since $\delta t_2$ is equal to the time interval observed by the observer at $r_0$, $\delta t_0$, we can find the proper time observed by the observer, $\delta \tau_0$ by simply inverting Eq (\ref{7}) and multiplying by $ \left( 1 - \frac{2M}{r_0} \right)^\frac{1}{2}$,

\begin{eqnarray}
	\delta \tau_0 & = & \delta t_0 \left( 1 - \frac{2M}{r_0} \right)^\frac{1}{2}, 	\nonumber	\\
	& =& \delta t_e \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right) \left( \frac{r_1 - 2(M-\Delta M)}{r_2 - 2(M - \Delta M)} \right) \left( 1 -\frac{2M}{r_0} \right) \right)^\frac{1}{2}. 
\end{eqnarray}

@@

This expression is exact in the limit that the observer is far away. By expressing the distances from the horizon as, 
\begin{eqnarray}
	r_1 & = & 2M + \epsilon 	\nonumber	\\
	 r_2 & = & 2M + \epsilon + \epsilon 	\label{11'},
\end{eqnarray}

we can write Eq (\ref{10}) as

\begin{equation}
	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} = \left( \left( \frac{\epsilon + \epsilon}{\epsilon} \right)^\frac{1}{2} \left( \frac{\epsilon + 2 \Delta M}{\epsilon + \epsilon + 2\Delta M} \right)^\frac{1}{2} - 1\right). \label{12}
\end{equation}

@@

\begin{equation}
	S^0_0 =  \frac{1}{4 \pi r_1} \left( \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} - \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} \right).
\end{equation}

This represents the surface energy density, to convert it to the energy of the shell, $\mathcal{E}$, we multiply by the surface area of the shell which is $4 \pi r_1^2$

\begin{equation}
	\mathcal{E} =  r_1 \left( \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} - \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} \right).	\label{19}
\end{equation}

@@

\begin{eqnarray}
	l & = & \int^{2M + \epsilon}_{2M} \frac{dr}{\left( 1 - \frac{2M}{r} \right)^\frac{1}{2}}	\nonumber	\\
	& = & (2M \epsilon)^\frac{1}{2}  + M \ln \left( \frac{M + \epsilon + (2M\epsilon)^\frac{1}{2}}{M} \right).	\label{20}
\end{eqnarray}

@@

\begin{eqnarray}
	\delta l & = & \int^{2M + \epsilon + \delta \epsilon}_{2M + \epsilon} \frac{dr}{\left(1 - \frac{2M'}{r} \right)^\frac{1}{2}} \nonumber	\\
	& = & (2M'(\epsilon + \delta \epsilon))^{\frac{1}{2}} + M' \ln \left(\frac{M' + \epsilon + \delta \epsilon + (2M'(\epsilon +\delta \epsilon))^{\frac{1}{2}}}{M'} \right) - (2M'\epsilon)^\frac{1}{2} - M' \ln \left( \frac{M' + \epsilon + (2M' \epsilon)^\frac{1}{2}}{M'} \right)	\label{21}
\end{eqnarray}

Eqs (\ref{19}, \ref{20}, \ref{21}) can be used in Eq (\ref{12}) to replace $\Delta M, \epsilon, \delta \epsilon$ respectively by the appropriate physical quantities. It is not possible to do this analytically but it can be done numerically. We show the plots of $\frac{\delta \tau_0 - \delta \bar{\tau_0}}{\delta \bar{\tau_0}}$ as functions of $M$. 
\\
\\
We can obtain analytic expressions in the limit that the shells are very close to the horizon and this is what is presented in the next section.

@@

In the near horizon limit we assume $\epsilon<< 2M$ and furthermore assume that the perturbations $\Delta M, \delta \epsilon$ are much smaller than $\epsilon$. Under these assumptions Eq (\ref{12}), to leading order om small quantities, becomes

@@

and the conversion to proper quantities from Eqs (\ref{19}, \ref{20}, \ref{21}) gives, to leading order,

\begin{equation}
	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} =  - \frac{\mathcal{E} \delta l}{l^2} = - \sigma \delta l \left( \frac{2M}{l} \right)^2
\end{equation}

where $\sigma \approx \frac{\mathcal{E}}{(2M)^2}$.

@@

>>>>

Classically, soft hairs manifest as memory effects that alters the distances between geodesics, which is very similar to the effect of geometric uncertainty as we showed in this paper.
Based on this picture, one may try to quantize the soft hairs and build a toy model that involves quantum interaction, therefore entanglement, between the soft hairs and the usual QFT modes.
That would provide a complete picture that the loss of subsystem unitarity is really just entanglement with another subsystem which was originally (and illegitimately, as we argued) assumed as the classical background.

@@

where the superscript represents particle $1$. An analogous geodesic equation is given for particle 2.

@@

%We can convert $\delta\bar{t_0}$ to proper time
%
%\begin{equation}
%	\delta \bar{\tau_0} = \left( 1 -\frac{2M}{r_0} \right)^\frac{1}{2} \delta \bar{t_0}
%\end{equation}
%
%and in the limit that the observer is very far away $\delta \bar{\tau_0} \approx \delta \bar{t_0}$.

@@

Since $\delta t_2$ is equal to the time interval observed by the observer at $r_0$, $\delta t_0$, we can find the proper time observed by the observer, $\delta \tau_0$,

\begin{equation}
	\delta \tau_0  = \delta t_e \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right) \left( \frac{r_1 - 2(M-\Delta M)}{r_2 - 2(M - \Delta M)} \right) \left( 1 -\frac{2M}{r_0} \right) \right)^\frac{1}{2}. 
\end{equation}

@@

This expression is exact in the limit that the observer is far away. By expressing the distances from the horizon as, $r_1  =  2M + \epsilon,  r_2  =  2M + \epsilon + \delta \epsilon$, we can write Eq (\ref{10}) as

\begin{equation}
	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} = \left( \left( \frac{\epsilon + \delta \epsilon}{\epsilon} \right)^\frac{1}{2} \left( \frac{\epsilon + 2 \Delta M}{\epsilon + \delta \epsilon + 2\Delta M} \right)^\frac{1}{2} - 1\right). \label{12}
\end{equation}

@@

\begin{equation}
	\sigma = S^0_0 =  \frac{1}{4 \pi r_1} \left( \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} - \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} \right).	\label{sig}
\end{equation}

%This represents the surface energy density, to convert it to the energy of the shell, $\mathcal{E}$, we multiply by the surface area of the shell which is $4 \pi r_1^2$
%
%\begin{equation}
%	\mathcal{E} =  r_1 \left( \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} - \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} \right).	\label{19}
%\end{equation}

@@

\begin{equation}
	l =  (2M \epsilon)^\frac{1}{2}  + M \ln \left( \frac{M + \epsilon + (2M\epsilon)^\frac{1}{2}}{M} \right).	\label{20}
\end{equation}

@@

\begin{equation}
	\delta l = (2M'(\epsilon + \delta \epsilon))^{\frac{1}{2}} + M' \ln \left(\frac{M' + \epsilon + \delta \epsilon + (2M'(\epsilon +\delta \epsilon))^{\frac{1}{2}}}{M'} \right) - (2M'\epsilon)^\frac{1}{2} - M' \ln \left( \frac{M' + \epsilon + (2M' \epsilon)^\frac{1}{2}}{M'} \right)	\label{21}
\end{equation}

Eqs (\ref{sig}, \ref{20}, \ref{21}) can be used in Eq (\ref{12}) to replace $\Delta M, \epsilon, \delta \epsilon$ respectively by the appropriate physical quantities. It is not possible to do this analytically but it can be done numerically. We show the plots of $\frac{\delta \tau_0 - \delta \bar{\tau_0}}{\delta \bar{\tau_0}}$ as functions of $M$. 
\\
\\
We can obtain analytic expressions in the limit that the shells are very close to the horizon and this is what is presented in the next section.

@@

In the near horizon limit we assume $\epsilon<< 2M$ and furthermore assume that the perturbations $\Delta M, \delta \epsilon$ are much smaller than $\epsilon$. Under these assumptions Eq (\ref{12}), to leading order in small quantities, becomes

@@

and the conversion to proper quantities from Eqs (\ref{sig}, \ref{20}, \ref{21}) gives, to leading order,

\begin{equation}
	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} \approx \frac{l}{4M} \sqrt{\frac{1}{(6 \pi \delta l \sigma - 1)^\frac{2}{3} -1 }} - 1.
\end{equation}

@@

\begin{figure}[h!]
\begin{center}.
\includegraphics[scale = 0.5]{tau_compare.pdf}
\caption{}
\label{}
\end{center}
\end{figure}
